Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-09 main.tex
Finished problem decomposition section - updated the start of the crypto section to suit the now moved decomposition discussion Updated the section summary to correctly summarise the new sections Added the notation paragraph Updated all Tikz images to be narrower as it looks nicer - also updated all the tikzimage .tex's to include preamble code so they look the same when opened in TikzEdt

% TODO update the below
In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties. Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it. Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme. In Section \ref{sec:sim_and_results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.

@@

\subsection{Notation}
Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list

@@

\section{Literature Overview}
In this section we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.

@@

\subsection{Problem Decomposition}
The recursive nature of the problem definition above complicated the definition and proof of security requirements.

We will instead decompose the communication part of the problem into a form of aggregation, which we can reason and prove more easily.

Due to the non-linearity of the measurement model \eqref{eqn:measurement_model}, we will use a linearisation

This type of linearisation will depend on the current state estimate and therefore requires communication between measurement producers and state estimators, in our case communication between the sensors and navigator

The basic idea of our aggregation decomposition is to formulate the computing of model linearisation with the ability to compute weighted sums of state-related information at sensors, and again summing

% note also the reason for not computing sums at the navigator (will require j sums to be sent rather than n)
% Possible as a remarkat the end? "We note that y= ... = ... and argue the benefit of this method depends on j >> n reducing communication costs

@@

    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms. As privacy-preserving implementations of such mechanisms require additional complications, we do not consider the scenario in this work.
    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents. We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
\end{description}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Sizes
    \tikzmath{\srange = 3.54; \sradius = 0.04;}
    % Sensor locations (sensor 3 is shared)
    \coordinate (s1) at (1.4086,-4.5869);
    \coordinate (s2) at (4.0633,-5.9948);
    \coordinate (s3) at (3.1235,-3.2054);
    \coordinate (s4) at (4.5563,-1.6861);
    \coordinate (s5) at (5.9909,-3.5635);
    % Navigator location
    \coordinate (nav_loc) at (4,-4);
    % Bounding rectangle
    \coordinate (brect_start) at (0,0);
    \coordinate (brect_end) at (8.0, -8.0);

@@

\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation. In the context of navigation, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$. This has been summarized in Figure \ref{fig:agg_steps}. In Section \ref{sec:private_localisation} we will show how this protocol can be sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.75]
    % Step 1
    \node at (5,22.5) {1. Broadcast and linear combinations step};
    % Navigator
    \node at (1.25,19.25) {Navigator};
    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
    % Sensors
    \node at (7.5,21.75) {Sensor $1$};
    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (7.5,14.75) {Sensor $n$};
    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (7.5,18.75) circle (0.05);
    \fill [black] (7.5,17.75) circle (0.05);
    \fill [black] (7.5,18.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};

    % Step 2
    \node at (5,13.25) {2. Aggregation step};
    % Navigator
    \node at (3.25,10.75) {Navigator};
    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (8.75,12.5) {Sensor $1$};
    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
    \node at (8.75,6.5) {Sensor $n$};
    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
    \fill [black] (8.75,10) circle (0.05);
    \fill [black] (8.75,9) circle (0.05);
    \fill [black] (8.75,9.5) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
    \node at (6.75,11.5) {$y_1^{(t)}$};
    \node at (6.75,7.5) {$y_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,23.25) rectangle (10,14.25);
    \draw [gray] (0,14) rectangle (10,5.5);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{Required linear-combination aggregation steps at time $t$.}
\label{fig:agg_steps}
\end{figure}

To perform the protocol from Figure \ref{fig:agg_steps} in a secure manner, we must first describe the security properties we aim to achieve. Broadly speaking, we want a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{description}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous timesteps, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous timesteps. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
\end{description}

@@

\subsection{Our Scheme} \label{sec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Bounding box
    \draw [gray] (0,-0.25) rectangle (8,7.5);

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);

    % Adversaries and challenger
    \node at (4,3.5) {\LARGE$\mathcal{A}'$};
    \node at (4,6) {\LARGE$\mathcal{A}$};
    \node at (4,0.5) {\LARGE$\mathcal{C}$};

@@

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5.5);

    \node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
    \draw [-latex] (6,5.5) -- (6,4.5);

    \node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (6,2.75) -- (6,1.75);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{High-level overview of our scheme's LCAO security proof.}
\label{fig:proof_summary}
\end{figure}

@@

    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{sec:our_scheme}. Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists. That is, there exists a negligible function $\eta$, such that
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
    \end{equation*}
    for security parameter $\kappa$. \qed
\end{pf}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}. We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}. Received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$. Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator. As was shown in Section \ref{sec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.

@@

\subsection{Algorithm} \label{subsec:algorithm}
In this section, we piece together our LCAO secure encryption scheme in Section \ref{sec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.

The privacy-preserving localisation filter can be described by the following steps.
\begin{description}
    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{sec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly. Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors. We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Prediction
    \draw [gray] (0,1.75) rectangle (8,8);
    \node at (4,7.5) {1. Prediction};

    % Navigator
    \fill  [blue!40] (3.25,7) rectangle (4.75,5.5);
    \pic[xscale=0.22,yscale=0.3] at (4,6.6725) {plane};
    \node at (4,5.875) {$\rvec{x}_k$, $\mat{P}_k$};

>>>>

The remainder of the paper is structured as follows. In Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties. Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it. Sections \ref{sec:loc_prelim} and \ref{sec:private_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the secure aggregation scheme. We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.

@@

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively. Encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$, respectively. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a | b$ stands for ``$a$ divides $b$'', and $a\|b$ for a bitwise concatenation of $a$ and $b$. Sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

\section{Literature Overview}
In this section, we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.

@@

\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
The recursive nature of the problem definition above complicates defining and proving of security requirements for the localisation scenario. As with existing estimation methods [] we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable. To support multiple aggregations at each time step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,-0.75) {2. Aggregation step};
    % Navigator
    \fill [blue!40] (1.375,-3) rectangle (5.125,-1.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-5.875) {Sensor $1$};
    \fill  (5.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \node at (5.25,-5.875) {Sensor $n$};
    \fill  (1.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-5.25) circle (0.05);
    \fill [black] (3.75,-5.25) circle (0.05);
    \fill [black] (3.25,-5.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
    \node at (2,-4) {$y_1^{(t)}$};
    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
    \node at (4.625,-4) {$y_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,0);
    \draw [gray] (0,-0.25) rectangle (6.5,-6.25);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{Required linear-combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}

In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.

\begin{rem}
    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement is computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
\end{rem}

@@

    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms. As privacy-preserving implementations of such mechanisms require additional complications, we do not consider the scenario in this work.
    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents. We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
\end{description}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize]
    % Sizes
    \tikzmath{\srange = 3.54; \sradius = 0.04;}
    % Sensor locations (sensor 3 is shared)
    \coordinate (s1) at (0.8523,-4.1508) {};
    \coordinate (s2) at (3.507,-5.5587) {};
    \coordinate (s3) at (2.5,-2.75) {} {};
    \coordinate (s4) at (4,-1.25) {};
    \coordinate (s5) at (5.4346,-3.1274) {};
    % Navigator location
    \coordinate (nav_loc) at (3.5,-3.25) {};
    % Bounding rectangle
    \coordinate (brect_start) at (0,0);
    \coordinate (brect_end) at (6.5, -6.5);

@@

\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our aggregation security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{description}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
\end{description}

@@

\subsection{Our Scheme} \label{subsec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Bounding box
    \draw [gray] (0,0) rectangle (6.5,6.5);

    % Outer adversary rectangle
    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
    % Inner adversary rectangle
    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);

    % Adversaries and challenger
    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};

@@

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5);

    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
    \draw [-latex] (4.5,5) -- (4.5,4.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{High-level overview of our scheme's LCAO security proof.}
\label{fig:proof_summary}
\end{figure}

@@

    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{subsec:our_scheme}. Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists. That is, there exists a negligible function $\eta$, such that
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
    \end{equation*}
    for security parameter $\kappa$. \qed
\end{pf}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Given our definitions for the aggregation scheme in Section \ref{subsec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}. We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}. Received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$. Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator. As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.

@@

\subsection{Algorithm} \label{subsec:algorithm}
In this section, we piece together our LCAO secure encryption scheme in Section \ref{subsec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.

The privacy-preserving localisation filter can be described by the following steps.
\begin{description}
    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly. Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors. We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Prediction
    \draw [gray] (0,2) rectangle (6.5,8);
    \node at (3.25,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [blue!40] (2.5,7) rectangle (4,5.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
    \node at (3.25,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
